\documentclass{article}

% If you're new to LaTeX, here's some short tutorials:
% https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes
% https://en.wikibooks.org/wiki/LaTeX/Basics

% Formatting
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[titletoc,title]{appendix}

% Math
% https://www.overleaf.com/learn/latex/Mathematical_expressions
% https://en.wikibooks.org/wiki/LaTeX/Mathematics
\usepackage{amsmath,amsfonts,amssymb,mathtools}

% Images
% https://www.overleaf.com/learn/latex/Inserting_Images
% https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions
\usepackage{graphicx,float}

% Tables
% https://www.overleaf.com/learn/latex/Tables
% https://en.wikibooks.org/wiki/LaTeX/Tables

% Algorithms
% https://www.overleaf.com/learn/latex/algorithms
% https://en.wikibooks.org/wiki/LaTeX/Algorithms
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algorithmic}

% Code syntax highlighting
% https://www.overleaf.com/learn/latex/Code_Highlighting_with_minted
\usepackage{minted}
\usemintedstyle{borland}

% References
% https://www.overleaf.com/learn/latex/Bibliography_management_in_LaTeX
% https://en.wikibooks.org/wiki/LaTeX/Bibliography_Management
\usepackage{biblatex}
\addbibresource{references.bib}

% Title content
\title{DSP 2020 Homework 1}
\author{Wu, Bo-Run r08942073}
\date{November 6, 2020}

\begin{document}

\maketitle

\begin{center}
    I mainly break this homework into two c files, train.c and test.c respectively.
\end{center}

% Training HMM
\section{Training HMM}

In train.c, I break the training procedure of Baum-Welch algorithm into several functions to calculate $\alpha$, $\beta$, $\gamma$, and $\epsilon$ separately.

First, I write forward and backward algorithms according to the equation listed in page 9 and page 10 of the homework assignment. The problem that I encounter is the logical error of my dynamic programming for each state. I forgot to add the initialization for the start of each state, causing the parameters to be accumulated during update. When the first time I go back and check the code in train.c is the testing results of the testing sequences. The results come out that all the testing results are all model\_01.txt. Then, I open the debugger to check for the each step to calculate the parameters, and it turns out that the $\alpha$ and $\beta$ are too big while the state get higher and higher.

After calculating $\alpha$ and $\beta$, I calculate the $\gamma$ value also according to the equation listed in page 11 of the homework assignment by $\alpha$ and $\beta$ matrices calculated from above. At the meantime, I also record the $\gamma$ value with different observations, and this matrix help us to update HMM model at the last state. Last, I calculate the $\epsilon$ value also according to the equation listed in page 12 of the homework assignment by the given $\alpha$ and $\beta$ matrices. Also, as in the $\gamma$, I also record the $\epsilon$ value with different states.

% Testing HMM  
\section{Testing HMM}

In test.c, I write the Viterbi algorithm as a function according to the equation listed in page 17 of the homework assignment. The problem that I encounter here is the index for $\delta$ value in the for loop, because there is too many nested for loop while calculating the $\delta$ value. I encounter many times with indexing out of matrix, causing the compile error while compiling.

\end{document}
