\documentclass{article}

% If you're new to LaTeX, here's some short tutorials:
% https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes
% https://en.wikibooks.org/wiki/LaTeX/Basics

% Formatting
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[titletoc,title]{appendix}

% Math
% https://www.overleaf.com/learn/latex/Mathematical_expressions
% https://en.wikibooks.org/wiki/LaTeX/Mathematics
\usepackage{amsmath,amsfonts,amssymb,mathtools}

% Images
% https://www.overleaf.com/learn/latex/Inserting_Images
% https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions
\usepackage{graphicx,float}

% Title content
\title{DSP 2020 Homework 3}
\author{Wu, Bo-Run r08942073}
\date{December 22, 2020}

\begin{document}

\maketitle

\begin{center}
  I break the viterbi algorithm for bi-gram into two parts, Forward and Backward
  parts. Besides, the mapping algorithm is listed in the third part.
\end{center}

% Viterbi forward
\section{Forward}
I write forward algorithm according to equation of the derivation from the Q\&A.
In order to calculate and record the graph of the results, I use two vector
score and path to record the details of the dynamic programming. While
calculating the score of the viterbi algorithm, I also record the path for
backward to trace the route and get the correct sequence that have the maximum
probability..

The issue that I ran into is the encoding problem. I accidentally open the file
with UTF-8 encoding and the mandarin character size of the UTF-8 is 3, instead
of 2, letting me stuck in this bug for at least 4 hours until I see the follow
up Q\&A to check the file type. Furthermore, It's also hard to design the way to
load the mapping files to transform different Zhuyin into different BIG5
character the correct character However, this time I learn the lesson from HW1
that I have to initialize the parameters every time calculating for dynamic
programming. 

% Viterbi backward
\section{Backward}
After calculating the forward part of the viterbi algorithm, I write a backward
algorithm to trace the route from the vector path to get the correct sequence. 

\section{Mapping}
I write the source code of mapping Zhuyin to BIG5 with python, using dictionary
and set data-structures to convert the mapping back.

\end{document}
